A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2018-06-16 Manuscript/vaught_2017.tex

\author{Joseph Hennawi}
\affiliation{Department of Physics, Broida Hall, University of California, Santa Barbara, CA 93106-9530}

@@

The mass and energy of galactic winds remain poorly constrained via traditional absorption line studies. One way to better constrain these parameters is to measure the spatial extent of the outflow in emission. We perform a VLT/FORS2 narrowband imaging of 5 star-forming galaxies at redshift $z=0.67-0.69$ in the GOODS-S field as part of an effort to spatially resolve and constrain the radial extent of large-scale outflows traced by \ion{Mg}{2} emission. These observations probe extended \ion{Mg}{2} emission down to unmatched surface brightness limits of 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ (5$\sigma$).  We do not detect any extended \ion{Mg}{2} emission in any of our galaxies, thus placing strong upper limits on the strength of \ion{Mg}{2} emission in the sample galaxies. Our observations allow us to create the first ever spatially-resolved map of \ion{Mg}{2} absorption, revealing approximately constant absorption strengths across the galaxy disks. Our detection limits in concert with a previous studies Keck/LRIS spectra allow us to model \ion{Mg}{2} emission for isotropic and anisotropic dust-free winds. We find that anisotropic winds reduce the strength of estimated missing \ion{Mg}{2} emission below our 5$\sigma$ limit.

@@

\keywords{galaxies: evolution, Galactic Winds}

@@

An accurate picture of what types of galaxies host outflows comes from numerous absorption line studies of galaxies (\citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}). Outflows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systematic velocity. Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^4$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) in \ion{Mg}{2} has revealed outflows in most galaxies that host active star-formation (e.g. \citethnop{chen2010}; \citethnop{Martin2012}; \citethnop{Rubin_2014}). Even though these probes can constrain: the radial velocity, column density and covering fraction of the flow, this method is weak in constraining the overall radial extent and provides no information on the morphology of the outflow.

@@

One proposed production mechanism for the galaxy's observed \ion{Mg}{2} line profile is photon scattering. In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions, $\lambda_{2796}$ and $\lambda_{2803}$. Once these transitions are excited, they may only decay back to the ground state and if the optical depth of the gas is high, then the gas will resonantly trap the absorbed photons. Because the photons are absorbed in the rest frame of the gas, the absorption will be blueshifted relative to the galaxy's systematic velocity. The \ion{Mg}{2} ions in the section of the wind farthest from the observer will absorb and scatter photons that are redshifted relative to the front portion of the wind. Because the photons are redshifted, the photons will be able to travel freely towards the observer through the wind to produce emission at and redward of the systematic velocity of the galaxy (\citethnop{Rubin_2011}, \citethnop{Prochaska_2011}). Since the first detection of \ion{Mg}{2} emission by \citeth{Rubin_2011}, a further detection of extended \ion{Mg}{2} emission is found in \cite{Martin2013}, where they observe \ion{Mg}{2} emission that extends $12-18$ kpc for the galaxy 32016857 at $z=0.9392$. Additionally, \ion{Mg}{2} is found in 1D and IFU spectra (\citethnop{Erb2012} and Feltre et. al (2018)). In these surveys of galaxies between with redshift $ 0.70 < z < 2.30$, \ion{Mg}{2} is detected in pure emission, pure absorption and with P-Cygni profiles. Detections of \ion{Mg}{2} in emission was found to be associated with galaxies of lower stellar mass and bluer spectral slopes.

Various models of galactic winds are explored in \citethnop{Prochaska_2011}. This analysis involved generating spectra for the  \ion{Mg}{2} and  \ion{Fe}{2}$^*$ transitions, using a set of radiative transfer algorithms, for an isotropic and anisotropic set of dust and dust-free winds. The authors demonstrated that isotropic dust-free winds will conserve photon flux, thus predicting that blueshifted absorption lines should be accompanied by emission profiles of winds with similar equivalent widths (EW). Anisotropic winds however were demonstrated to significantly weaken emission at strengths proportional to the angular extent of the wind. The scattered emission was additionally weakened by the inclusion of dust and the affect of a strong interstellar medium (ISM).

In this paper, we present the first narrowband imaging of \ion{Mg}{2} line emission around 5 star-forming  galaxies located in the deep Great Observatories Origins Deep Survey south (GOODS-S) field at redshift $z \sim 0.7$. The value in using narrowband imaging is the ability to spatially resolve any absorption and emission from a galaxy. We use two filters: a line filter and a continuum filter. The line filter covers the \ion{Mg}{2} doublet, while the continuum filter is off-set from line filter. The continuum filter will allow us to observe the continuum level of the galaxy near the \ion{Mg}{2} doublet. With the resulting images taken using the two filters, we can subtract the continuum image from the \ion{Mg}{2} image, effectively creating an image that contains only photons from \ion{Mg}{2}. Contrary to 1D spectra, the narrowband imaging has the ability to measure the surface brightness, optical depth and radial extent of a wind. This narrowband imaging will allow us to create the first ever spatially resolved map of \ion{Mg}{2} emission.

In Section \ref{sec:obs_red} we describe our sample of GOOD-S galaxies, Keck/LRIS spectra as well as our VLT/FORS2 observations, imaging, and absolute flux calibration. We go into detail in our method of image subtraction in Section \ref{sec.cont_sub}. The analysis of these data are included in Section \ref{sec:analysis}, in detail we discuss the production surface bright profiles and limits for each galaxy, as well as the production of narrowband measured equivalent widths. Section \ref{sec:results} contains the results from our narrowband imaging analysis. We compare our SB detections limits to previous detections of extended \ion{Mg}{2} emission, additionally we compare our observations to predictions made by radiative transfer models in Section \ref{sec:discussion}. We conclude this paper in Section \ref{sec:conclusion}.
We adopt a $\Lambda$CDM cosmology with $h_{70} = H_0/(70\ \rm{ km}\ \rm{ s}^{-1}\ \rm{ Mpc}^{-1})$, $\Omega_{\rm{M}}= 0.3$, and $\Omega_{\Lambda} = 0.7$.

\section{Observations and Data Reduction}\label{sec:obs_red}
\subsection{Sample Selection}
Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep \emph{HST}/ACS imaging (Rubin et al. 2014)\nocite{Rubin_2014}.  In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}) and the AEGIS survey field (the Extended Groth Strip; Davis et al. 2007)\nocite{Davis2007}.  In inspecting the redshift distribution of the portion of this sample observable from the Southern Hemisphere, we uncovered a narrow peak of nine galaxies in the interval $0.66 < z < 0.68$.  This peak is in fact the global maximum of the distribution, as all other bins of width $\Delta z = 0.02$ have at most four galaxies.  Moreover, there are two narrow interference filters available on VLT/FORS2 centered at $\lambda \sim 468.4$ and 472.6 nm which cover the \ion{Mg}{2} $\lambda \lambda 2796, 2803$ transition in precisely this redshift interval.  We selected our final sample of five of these galaxies at $0.66 < z < 0.68$ to be close on the sky such that they could be imaged in a single $7' \times 7' $ FORS2 pointing.

@@

\subsection{VLT/FORS2 Observations}
Our barrow-band imaging data were taken in service-mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\sim0.7$ (see Table \ref{tab:filters}). The filter transmission curves are plotted along with each galaxy's spectrum in Figure~\ref{fig:spec_images}.

FORS2 has a pixel scale of $0.25''$ pixel$^{-1}$ and a field of view of $7'\times7'$ with $2 \times 2$ binning. Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A). The seeing (see Figure \ref{fig.seeing}) ranged from 0.5 arcsec to 2.5 arcsec. The data were taken with three pointings offset by 0.25' East/West with exposure times of $\approx$ 1000 s. A total of 38  exposures were taken in each filter. Summing the individual exposure times for each filter results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.

@@

\begin{figure*}[!h]
\centering
\gridline{\fig{../Figures/filt_26_spectra.pdf}{0.5\textwidth}{(a)}
          \fig{../Figures/filt_36_spectra.pdf}{0.5\textwidth}{(b)}}
\gridline{\fig{../Figures/filt_03_spectra.pdf}{0.5\textwidth}{(c)}
          \fig{../Figures/filt_64_spectra.pdf}{0.5\textwidth}{(d)}}
           \fig{../Figures/filt_57_spectra.pdf}{0.5\textwidth}{(e)}
\caption{Keck/LRIS spectra of the sample galaxies and the transmission curves of the filters HeII+47 (blue dashed line) and HeII/3000+48 (red dashed line) . The left-hand axis is in units of flux density and the right-hand axis is the percentage of light transmitted the filter at each wavelength. Vertical dashed lines indicate the wavelength of the redshifted \ion{Mg}{2}\ doublet. The \ion{Mg}{2}\ doublet falls fortuitously at the central wavelength of the HEII+47 filter.}
\label{fig:spec_images}
\end{figure*}

@@

\subsection{Supplemental Keck/LRIS spectra}
In addition to VLT imaging, in the present analysis we utilize galaxy spectra taken from the \cite{Rubin_2014} Keck I Low Resolution Imaging Spectrometer (LRIS) program. A $0.9''$ slit width was used for all slitmasks and the median FWHM resolution for the spectra is 274 km s$^{-1}$ at $\lambda_{\rm rest} \approx$ 2800 \AA\ and $286\mkms$  at $\lambda_{\rm rest}\approx$ 2600 \AA\ (see Figure \ref{fig:spec_images}).

\subsection{Image Reduction}
The data were reduced using custom routines written in \textbf{Python}. 
The images were first corrected by subtracting and removing the overscan region of the CCD. 
Then the images were bias-subtracted and flat-fielded using twilight flats.
To improve the flat-fielding essential for detecting faint extended emission across the fields,we further correct for the illumination patterns using night-sky flats. The night-sky flats were produced by combining the unregistered science frames with an average sigma-clipping algorithm after masking out all the objects, and any bad pixels. Each individual image was cleaned of cosmic rays and bad pixels by utilizing the \emph{L.A. Cosmic} algorithm \citep{Dokkum2001}.
The astrometry solutions were calculated via Astrometry.net (Lang et al. 2010)\nocite{Lang}, yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$. Before image stacking, we ran each frame through \emph{SExtractor} \citeth{Bertin} in order to create a root mean square (RMS) map of each science image.

The final stacked image for each filter is obtained using \emph{SWarp} \citeth{Bertin}.
Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted (Arrigoni Battaia et al. 2015) \nocite{Battaia_2015}. 
The frames, after background-subtraction, are resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
The images are average-combined and weighted by the night-flat image in order to increase the signal-to-noise of any \ion{Mg}{2} emission. Additionally, \emph{SWarp} generates a final set of RMS image from the night flats and the combination of RMS images for individual science frames. Our final stacked images in each filter are shown in Figure~\ref{fig:stacked_image} with the target galaxies indicated.

@@

\begin{table*}[t]
\centering
\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW ( in the observed frame) include both components of the \ion{Mg}{2} doublet and were calculated with Eq. \ref{eq:specEW} and the supplemental Keck/LRIS spectra.}
\begin{tabular}{lllllll} \hline \hline
Object & R.A. & Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) \smallskip      \\ \hline 
J033225.26-      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$\\ 
274524.0     & &  &  &         \\
J033231.36-      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$\\
274725.0      & &  &   &        \\
J033230.03-      & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$\\
274347.3      & &  &   &        \\
J033229.64-      & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$\\
274242.6     & &  &     &      \\
J033230.57-      & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ \\
274518.2      & &  &  &         \\ \hline 
\end{tabular}
\label{tab:prop}
\end{table*}

@@

\section{Image Subtraction}\label{sec.cont_sub}

\subsection{Spectral Correction}
In preparation for continuum subtraction, we first consider whether the continuum level of each galaxy spectrum changes significantly over the passbands of our two filters.
We use the supplementary spectra from \citeth{Rubin_2014}, to fit the continuum and determine the spectral slope of each galaxy. We use the interactive fitting routine \emph{lt\_continuumfit} from the \emph{linetools} package (Prochaska et al. 2016)\footnote{https://github.com/linetools/linetools}\nocite{Prochaska2016} to fit the continuum. We then find the total continnum flux in each filter by convolving the fitted continuum with each filter's transmission curve. Next, we take the ratio of both integrated totals, as the ratio will indicate the scaling factor needed to correct our flux measurements prior to continuum subtraction. Comparing these ratios between each galaxy, we find that they are effectively the same, within 0.1\%, with a value of 1.118. This value is equal to the ratio between the FWHM of the filter transmission curves, allowing us to conclude that the slope of the spectrum of each galaxy is flat, and hence that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.

\subsection{Continuum Subtraction}
To properly continuum-subtract the image taken with the on-line filter in excess of the continuum, we follow a prescription given by \cite{Battaia_2015}. 
We first determine the continuum flux density from the off-\ion{Mg}{2} filter,
\begin{equation}
f_{\rm{cont}}=\frac{F_{\rm{cont}}}{\Delta \lambda_{\rm{cont}}},
\end{equation}\\
where $F_{\rm{cont}}$ and $\Delta \lambda_{\rm{cont}}$ are the observed flux per pixel of the continuum image and the transmission FWHM of the continuum filter, respectively. With $f_{cont}$ it is then possible to calculate the flux of any excess emission, $F_{\rm{line}}$:
\begin{equation}
F_{\rm{line}}=F_{\rm{MgII}}-f_{\rm{cont}} \Delta \lambda_{\rm{MgII}}
\label{eq:subtraction}
\end{equation}
where $F_{\rm{MgII}}$ and $\Delta \lambda_{MgII}$ are the observed flux per pixel in the \ion{Mg}{2} filter and the transmission FWHM of the \ion{Mg}{2} filter. The continuum subtracted images of each galaxy are shown in Fig. \ref{fig:stamp_images}. The continuum subtracted image has uniform background and no obvious signatures of emission.

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.7]{../Figures/stamps.pdf}
\caption{ $10'' \times 10''$ images of each galaxy in our sample. Top row: Continuum surface brightness in ergs/s/cm$^2$/sq.arcsec. Bottom row: Continuum subtracted \ion{Mg}{2} surface brightness.  Absorption can be seen in 4 of 5 galaxies. The red contours represent the outline of the 1$\sigma$ surface brightness limit in the HeII/3000+38 image, defined in Sec. \ref{sec.sb}. The colorbar shows the scaling used for the \ion{Mg}{2} images.}
\label{fig:stamp_images}
\end{figure*}

>>>>

\author{Joseph F. Hennawi}
\affiliation{Department of Physics, Broida Hall, University of California, Santa Barbara, CA 93106-9530}

@@

The mass and energy of galactic winds remain poorly constrained via traditional absorption line studies. One way to better constrain these parameters is to measure the spatial extent of the outflow in emission. We perform a VLT/FORS2 narrowband imaging of 5 star-forming galaxies at redshift $z=0.67-0.69$ in the GOODS-S field as part of an effort to spatially resolve and constrain the radial extent of large-scale outflows traced by \ion{Mg}{2} emission. These observations probe extended \ion{Mg}{2} emission down to unmatched surface brightness limits of 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ (5$\sigma$).  We do not detect any extended \ion{Mg}{2} emission in any of our galaxies, thus placing strong upper limits on the strength of \ion{Mg}{2} emission at projected distances $R_{\perp} = 8-21$ kpc from the sample galaxies. Our observations allow us to create the first ever spatially-resolved map of \ion{Mg}{2} absorption, revealing approximately constant absorption strengths across the galaxy disks. Our detection limits in concert with a previous studies Keck/LRIS spectra allow us to model \ion{Mg}{2} emission for isotropic and anisotropic dust-free winds. We find that anisotropic winds reduce the strength of estimated missing \ion{Mg}{2} emission below our 5$\sigma$ limit.

@@

\keywords{galaxies: evolution, galaxies: absorption lines}

@@

An accurate picture of what types of galaxies host outflows comes from numerous absorption line studies of galaxies (\citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}). Outflows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systematic velocity. Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^2$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) in \ion{Mg}{2} has revealed outflows in most galaxies that host active star-formation (e.g. \citethnop{chen2010}; \citethnop{Martin2012}; \citethnop{Rubin_2014}). Even though these probes can constrain: the radial velocity, column density and covering fraction of the flow, this method is weak in constraining the overall radial extent and provides no information on the morphology of the outflow.

@@

One proposed production mechanism for the galaxy's observed \ion{Mg}{2} line profile is photon scattering. In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions, $\lambda_{2796}$ and $\lambda_{2803}$. Once these transitions are excited, they may only decay back to the ground state and if the optical depth of the gas is high, then the gas will resonantly trap the absorbed photons. Because the photons are absorbed in the rest frame of the gas, the absorption will be blueshifted relative to the galaxy's systematic velocity. The \ion{Mg}{2} ions in the section of the wind farthest from the observer will absorb and scatter photons that are redshifted relative to the front portion of the wind. Because the photons are redshifted, the photons will be able to travel freely towards the observer through the wind to produce emission at and redward of the systematic velocity of the galaxy (\citethnop{Rubin_2011}, \citethnop{Prochaska_2011}). Since the first detection of \ion{Mg}{2} emission by \citet{Rubin_2011}, another detection was reported by \cite{Martin2013}, who observed \ion{Mg}{2} emission that extends $12-18$ kpc from a strongly star-forming galaxy
at $z=0.9392$.   \ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with Keck/DEIMOS and VLT/MUSE  (\citethnop{Erb2012} and Feltre et. al (2018)). These surveys, which include galaxies with redshifts $ 0.70 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles.  Detections of \ion{Mg}{2} in emission were found to be associated with galaxies of lower stellar mass and bluer spectral slopes.

The diversity of these spectral profiles may be understood using radiative transfer modeling of galactic winds.
%Various models of galactic winds are explored in 
\citet{Prochaska_2011} have used this technique to predict 
%This analysis involved generating 
spectra for the  \ion{Mg}{2} and  \ion{Fe}{2}$^*$ transitions for a variety of wind morphologies.
%, using a set of radiative transfer algorithms, for an isotropic and anisotropic set of dust and dust-free winds. 
The authors demonstrated that isotropic dust-free winds will conserve photon flux, thus predicting that blueshifted absorption lines should be accompanied by emission profiles of winds with similar equivalent widths (EW). Anisotropic winds, however, were demonstrated to exhibit significantly weaker emission at strengths proportional to the angular extent (i.e., solid angle) of the wind. The scattered emission was additionally weakened by the inclusion of dust and the presence of a strongly-absorbing interstellar medium (ISM).
Thus, spatially-resolved measurement of the surface brightness of this emission constrains not only the radial extent of the emitting material, but also its morphology and dust content.

In this paper, we present the first narrowband imaging of the \ion{Mg}{2} transition around 5 star-forming  galaxies located in the Great Observatories Origins Deep Survey south (GOODS-S) field at redshift $z \sim 0.7$. 
%The value in using narrowband imaging is the ability to spatially resolve any absorption and emission from a galaxy. 
We use two filters: a line filter and a continuum filter. The line filter covers the \ion{Mg}{2} doublet, while the continuum filter is offset from the line filter by ${\sim}47$ \AA.    
The resulting imaging in each filter has a total integration time of 10 hrs.
%The continuum filter allows us to observe the continuum level of the galaxy near the \ion{Mg}{2} doublet. With the resulting images taken using the two filters, we can subtract the continuum image from the \ion{Mg}{2} image, effectively creating an image that contains only photons from \ion{Mg}{2}. 
As opposed to 1D spectra, the narrowband imaging constrains the surface brightness, optical depth and radial extent of the wind. This narrowband imaging allows us to create the first ever high-S/N spatially resolved map of \ion{Mg}{2} emission and absorption.

In Section \ref{sec:obs_red} we describe our sample of GOOD-S galaxies, supplemental Keck/LRIS spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration. We go into detail in our method of continuum subtraction in Section \ref{sec.cont_sub}. The analysis of these data is presented in Section \ref{sec:analysis}, 
including our methods for calculating surface brightness profiles and detection limits for each galaxy, as well as maps of \ion{Mg}{2} equivalent widths.
%in detail we discuss the production surface bright profiles and limits for each galaxy, as well as the production of narrowband %measured equivalent widths. 
Section \ref{sec:results} presents results from our narrowband imaging analysis. We compare our SB detection limits to previous detections of extended \ion{Mg}{2} emission,  and compare our observations to predictions made by radiative transfer models in Section \ref{sec:discussion}. We conclude this paper in Section \ref{sec:conclusion}.
We adopt a $\Lambda$CDM cosmology with $h_{70} = H_0/(70\ \rm{ km}\ \rm{ s}^{-1}\ \rm{ Mpc}^{-1})$, $\Omega_{\rm{M}}= 0.3$, and $\Omega_{\Lambda} = 0.7$.

\section{Observations and Data Reduction}\label{sec:obs_red}
\subsection{Sample Selection}
Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep \emph{HST}/ACS imaging (Rubin et al. 2014)\nocite{Rubin_2014}.  In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}) and the AEGIS survey field (the Extended Groth Strip; Davis et al. 2007)\nocite{Davis2007}.  In inspecting the redshift distribution of the portion of this sample observable from the Southern Hemisphere, we uncovered a narrow peak of nine galaxies in the interval $0.66 < z < 0.68$.  This peak is in fact the global maximum of the distribution, as all other bins of width $\Delta z = 0.02$ have at most four galaxies.  Moreover, there are two narrow interference filters available on VLT/FORS2 centered at $\lambda \sim 4675$ and 4722 \AA\ which cover the \ion{Mg}{2} $\lambda \lambda 2796, 2803$ transition in precisely this redshift interval.  We selected our final sample of five of these galaxies at $0.66 < z < 0.68$ to be close on the sky such that they could be imaged in a single $7' \times 7' $ FORS2 pointing.  
We show color {\it HST}/ACS images of these objects in Figure~\ref{fig:hstims}.

@@

\subsection{VLT/FORS2 Observations}
Our narrow-band imaging data were taken in service-mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\sim0.7$ (see Table \ref{tab:filters}). The filter transmission curves are plotted along with each galaxy's spectrum in Figure~\ref{fig:spec_images}.
In the following, we will often refer to the HeII+47 filter as the ``line'' or \ion{Mg}{2} filter and the HeII/3000+48 filter as the ``continuum'' filter.

FORS2 has a native pixel scale of $0.125''$ pixel$^{-1}$ and a field of view of $7'\times7'$.  The data were taken with 
the CCD binned $2\times2$, yielding a pixel scale of $0.25''$ pixel$^{-1}$.
Images of three pointings offset by $0.25\arcmin$ East/West were obtained, with individual exposure times of $\approx$ 1000 sec.  A total of 38  exposures were taken in each filter. 
Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A). The seeing (see Figure \ref{fig.seeing}) ranged from $0.5\arcsec$ to $2.5\arcsec$. Summing the individual exposure times for each filter results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.

@@

\begin{figure*}[!h]
\centering
\gridline{\fig{../Figures/filt_26_spectra.pdf}{0.5\textwidth}{(a)}
          \fig{../Figures/filt_36_spectra.pdf}{0.5\textwidth}{(b)}}
\gridline{\fig{../Figures/filt_03_spectra.pdf}{0.5\textwidth}{(c)}
          \fig{../Figures/filt_64_spectra.pdf}{0.5\textwidth}{(d)}}
           \fig{../Figures/filt_57_spectra.pdf}{0.5\textwidth}{(e)}
\caption{Keck/LRIS spectra of the sample galaxies and the transmission curves of the filters HeII+47 (blue dashed line) and HeII/3000+48 (red dashed line) . The left-hand axis is in units of flux density and the right-hand axis is the percentage of light transmitted by the filter at each wavelength. Vertical dashed lines indicate the wavelengths of the redshifted \ion{Mg}{2}\ doublet. The \ion{Mg}{2}\ doublet falls fortuitously at the central wavelength of the HeII+47 filter for the galaxies shown in panels (a) through (d).}
\label{fig:spec_images}
\end{figure*}

@@

\subsection{Supplemental Keck/LRIS spectra}
In addition to VLT imaging, in the present analysis we utilize galaxy spectra taken from the \cite{Rubin_2014} Keck I Low Resolution Imaging Spectrometer (LRIS) program.  A $0.9''$ slit width was used for all slitmasks and the median FWHM resolution for the spectra is 274 km s$^{-1}$ at $\lambda_{\rm rest} \approx$ 2800 \AA\ and $286\mkms$  at $\lambda_{\rm rest}\approx$ 2600 \AA\ (see Figure \ref{fig:spec_images}).  The spectral coverage of these data extends from ${\sim}3200$ to 8000 \AA.

\subsection{Image Reduction}
The data were reduced using custom routines written in \textbf{Python}. 
The images were first corrected by subtracting and removing the overscan region of the CCD. 
Then the images were bias-subtracted and flat-fielded using twilight flats.
To improve the flat-fielding essential for detecting faint extended emission across the fields,we further correct for the illumination patterns using night-sky flats. The night-sky flats were produced by combining the unregistered science frames with an average sigma-clipping algorithm after masking out all the objects, and any bad pixels. Each individual image was cleaned of cosmic rays and bad pixels by utilizing the \emph{L.A. Cosmic} algorithm \citep{Dokkum2001}.
The astrometry solutions were calculated via Astrometry.net (Lang et al. 2010)\nocite{Lang}, and yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$. Before image stacking, we ran each frame through \emph{SExtractor} \citeth{Bertin} in order to create a root mean square (RMS) map of each science image.

The final stacked image for each filter is obtained using \emph{SWarp} \citeth{Bertin}.
Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted (Arrigoni Battaia et al. 2015)\nocite{Battaia_2015}. 
The frames, after background-subtraction, are resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
The images are weighted by the night-flat image and then  average-combined  in order to increase the signal-to-noise of any \ion{Mg}{2} emission. Additionally, \emph{SWarp} generates stacked RMS images by propagating the error images for each science frame.
%weighting and average-combining the RMS images for individual science frames.
 %from the night flats and the combination of RMS images for individual science frames. 
Our final stacked images in each filter are shown in Figure~\ref{fig:stacked_image} with the target galaxies indicated.

@@

\begin{table*}[t]
\centering
\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) include both components of the \ion{Mg}{2} doublet and were %calculated with Eq. \ref{eq:specEW} and 
determined from analysis of 
the supplemental Keck/LRIS spectra.}
\begin{tabular}{lllllll} \hline \hline
Object & R.A. & Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) \smallskip      \\ \hline 
J033225.26-274524.0      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$\\ 
%274524.0     & &  &  &         \\
J033231.36-274725.0       & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$\\
%274725.0      & &  &   &        \\
J033230.03-274347.3       & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$\\
%274347.3      & &  &   &        \\
J033229.64-274242.6      & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$\\
%274242.6     & &  &     &      \\
J033230.57-274518.2      & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ \\
%274518.2      & &  &  &         \\ 
\hline 
\end{tabular}
\label{tab:prop}
\end{table*}

@@

\section{Image Subtraction}\label{sec.cont_sub}
We have two goals for our study: (1) assess the surface brightness of line emission in the \ion{Mg}{2} transition in and around each target galaxy; and (2) spatially resolve the morphology of the strong \ion{Mg}{2} absorption observed against the galaxy continua.
To reach both of these goals, we must perform accurate subtraction of the continuum flux of each object from the filter covering the targeted line emission. For four of the five objects in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame.

\subsection{Spectral Correction}
In preparation for continuum subtraction, we first consider whether the continuum level of each galaxy spectrum changes significantly over the passbands of our two filters.
We use the supplementary spectra from \citet{Rubin_2014} to fit the continuum and determine the spectral slope of each galaxy. We use the interactive fitting routine \emph{lt\_continuumfit} from the \emph{linetools} package (Prochaska et al. 2016)\footnote{https://github.com/linetools/linetools}\nocite{Prochaska2016} to fit the continuum. We then find the total continuum flux in each filter by convolving the fitted continuum with each filter's transmission curve. Next, we take the ratio of both integrated totals, as the ratio will indicate the scaling factor needed to correct our flux measurements prior to continuum subtraction. Comparing these ratios between each galaxy, we find that they are effectively the same, within 0.1\%, with a value of 1.118. This value is equal to the ratio between the FWHM of the filter transmission curves, allowing us to conclude that the slope of the spectrum of each galaxy is flat, and hence that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.

\subsection{Continuum Subtraction}\label{subsec.cont_sub}

To properly continuum-subtract the image taken with the \ion{Mg}{2} filter, we follow a prescription given by \cite{Battaia_2015}. 
We first determine the continuum flux density from the continuum filter,
\begin{equation}
f_{\rm{cont}}=\frac{F_{\rm{cont}}}{\Delta \lambda_{\rm{cont}}},
\end{equation}\\
where $F_{\rm{cont}}$ and $\Delta \lambda_{\rm{cont}}$ are the observed flux per pixel of the continuum image and the transmission FWHM of the continuum filter, respectively. With $f_{\rm cont}$ it is then possible to calculate the flux of any excess emission, $F_{\rm{line}}$:
\begin{equation}
F_{\rm{line}}=F_{\rm{MgII}}-f_{\rm{cont}} \Delta \lambda_{\rm{MgII}}
\label{eq:subtraction}
\end{equation}
where $F_{\rm{MgII}}$ and $\Delta \lambda_{\rm MgII}$ are the observed flux per pixel in the \ion{Mg}{2} filter and the transmission FWHM of the \ion{Mg}{2} filter. The continuum subtracted images of each galaxy are shown in Figure \ref{fig:stamp_images}. The continuum subtracted image has uniform background and no obvious signatures of emission.
